%-------------------------
% ATS-Friendly Resume
% Author: Aayush Laddha
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & \textbf{\small #2} \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & \textbf{\small #2}\\\end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Aayush Laddha} \\ \vspace{1pt}
    Kolkata, West Bengal, India \\ \vspace{1pt}
    \small \href{tel:+918420996300}{\raisebox{-0.1\height}\faPhone\ \ \underline{+91 8420996300}} ~ \href{mailto:aayushladdha001@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aayushladdha001@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/imagiwaeve}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/imagiwaeve}}
    \vspace{-8pt}
\end{center}

\section{Professional Summary}
\small{Full-Stack Developer focused on shipping fast and solving real-world problems through AI, IoT, and automation. Currently building projects involving agentic AI, real-time systems, and IoT automation. Experienced in building scalable full-stack applications with React, Node.js, and LangChain, with a proven track record in international hackathons.}
\vspace{-10pt}

\section{Technical Skills \& Hard Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{ATS Matched Skills}{: React, Next.js, Node.js, Express, Tailwind CSS, Git, GitHub, MongoDB, PostgreSQL, Problem-solving} \\
     \textbf{Development Frameworks}{: React.js, Next.js, Node.js, Express.js, MERN Stack} \\
     \textbf{Languages \& Hard Skills}{: JavaScript, Python, HTML5, CSS3, C, MongoDB, RESTful APIs} \\
     \textbf{AI/ML \& Automation}{: LangChain, LangSmith, LangGraph, RAG, Vector Databases, Embedding Model} \\
     \textbf{IoT \& Systems}{: IoT Architecture, ESP32/Arduino, MQTT, Sensors Integration, Real-time Systems} \\
     \textbf{Tools \& Databases}{: MongoDB, Git, GitHub, Chrome Extensions, Postman}
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Professional Experience}
  \resumeSubHeadingListStart
\resumeSubheading{Founder \& Full-Stack Developer}{Dec 2025 - Present}{Imagiwaeve Studios}{India}
\resumeItemListStart
\resumeItem{Founded a web, AI, and automation agency, leading technical projects and client acquisition for scalable solutions.}
\resumeItem{Architected modern UI/UX using contemporary design principles, enhancing user engagement and product performance.}
\resumeItemListEnd
\resumeSubheading{Full Stack Developer}{September 2025 - Present}{KLYRO LABS}{India}
\resumeItemListStart
\resumeItem{Developed full-stack applications and rapid prototypes, integrating AI, IoT, and automation for client projects.}
\resumeItem{Utilized React and Node.js to ship high-performance, real-time systems, optimizing operational efficiency.}
\resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Gigfr} $|$ \footnotesize\textit{Next.js, Tailwind CSS, Node.js}}{}
\resumeItemListStart
\resumeItem{Developed a full-stack freelance platform, implementing robust backend logic and modern frontend interfaces.}
\resumeItem{Engineered a dynamic database schema and integrated escrow payment gateways for secure transactions.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{BioSentinel} $|$ \footnotesize\textit{React, Node.js, MongoDB, Groq API, Firebase}}{}
\resumeItemListStart
\resumeItem{Integrated NASA FIRMS and MOSDAC APIs for real-time geospatial intelligence and satellite monitoring of wildfires.}
\resumeItem{Developed 'Kaya,' a low-latency conversational AI assistant using Groq API for real-time species insights and data access.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Techno Main - Salt Lake}{June 2025 -- June 2029}
      {Bachelor of Computer Application - BCA(H), Computer Engineering}{Kolkata, West Bengal}
    \resumeSubheading
      {Dreamland School}{April 2023 -- May 2025}
      {Higher Secondary Education -- Computer Science}{West Bengal}
  \resumeSubHeadingListEnd 
\vspace{-16pt}

\section {Achievements \& Certifications}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf {Hackathon Success:} 1x Winner, 6x Finalist (including International: GenAI Exchange, Cardano)\\
         \textbf{Certifications:} Certificate of Excellence in CodeSpark (72-Hour Build Challenge), Tata GenAI Data Analytics, IIT Kanpur Antaragni Code Championship 2024, SuPrathon 2K25 \\
         \textbf{Volunteer Work:} Volunteer at Samarth TMSL (October 2025 - Present)\\
        }}
    \end{itemize}
 \vspace{-16pt}

\end{document}